Revisiting 'Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-05-19 analysis/quarto/paper.qmd
work on transpercy section

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, may not necessarily prevent us from reaching these targets, but it makes it more difficult in the future. Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals. This apllies especially to carbon dioxide emissions where its current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].

@@

Taken together, this study makes three contributions. First, it replicates parts of GMTV's original experiment and highlights the importance of pure replications. Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers. Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample. After reporting the methods, this paper is organized along these findings.

@@

In fact, the experiment reported in this article qualifies for the label _'pre-registered'_ at a first glance:
Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration]. In addition, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.].

The analysis that made the most sense after having collected the data is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability. Hence, this article combines both confirmatory as well as exploratory research.

Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent and easy to assess, showcasing (a), (b) and the transition from (a) to (b).

@@

In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game. The pure reproduction re-analyzes the original data. [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper. The scientific replication, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.

@@

## Pre-registered GMTV Replication {#sec-replication}

@@

First, I ask whether the samples differ with respect to their initial contributions to the public good. Is the replication sample (consisting of both students and non-students) more pro-social than the original sample? A two-sided rank sum test reveals that it is not (p=`r rs1`). Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean). Moreover, both samples' initial contributions resemble initial contributions participants usually make in the static game with partner matching.^[See Figure 3B in @fehrgaechter2000 [p.989], for instance.] However, in the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially. Do the two groups remain similar over the course of time?

@@

ggplot(data = R1[treatment != "noPunish15"],
       mapping = aes(x = ownContribution, fill = treatment, lty = treatment)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, 20),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, 0.1),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("Original Sample", "Replication Sample")) +
  guides(lty = "none") +
  geom_vline(xintercept = R1[treatment == "replication", 
                             mean(ownContribution)],
             col = "#FFFFFF",
             lty = 2) +
  geom_vline(xintercept = R1[treatment == "noPunish10", 
                             mean(ownContribution)],
             col = "#FFFFFF",
             lty = 1) +
    labs(title = "", 
       y = "", x = "Initially Contributed Tokens",
       caption = "White lines indicate means (dashed line = replication sample).") +
  layout +
  theme(legend.position = "top")
```

@@

In particular, do the two samples' contributions follow the same path over the 10 periods they played? The answer is _no_. @fig-share-of-contributions illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between. More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the replication sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`. ] For this reason, the original sample's behavior differs from the replication sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the replication sample's contributions flatten).

Note that increasing contributions over time imply increasing endowments over time. Hence, absolute contributions do not tell much about the willingness to cooperate. For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time. Both samples exhibit a similar pattern: their share of endowments contributed declined and did not stabilize. However, both samples also differ with respect to one aspect: the replication sample's share of contributions declines faster. This is mirrored by a two-sided rank sum test which is only significant at a five percent level in periods three and four.

@@

p1 <- ggplot(data = SUM, 
             aes(x = round, y = contribution, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="top") +
  geom_line(show.legend=FALSE) +
  geom_point() +
  scale_x_continuous(name="",  breaks = 1:15) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Average Amount of Tokens contributed") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Replication Sample")) + 
  guides(fill = "none") +
  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))

@@

p2 <- ggplot(data = SHARE, 
             aes(x = round, y = share, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="bottom") +
  geom_line(show.legend=FALSE) +
  geom_point() +
  scale_x_continuous(name="",  breaks = 1:15) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Share of Current Endowment contributed") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Replication Sample")) +
  guides(fill = "none")

@@

How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more, one would expect the respective groups to be  more wealthy. A mere mean comparison indicates just that: An average group in the original sample accumulated about `r round(originalWealth)` tokens. In contrast, an average group in the replication sample accumulated about `r round(replicationWealth)` tokens. This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last period of the game.

@@

ggplot(data = main,
       mapping = aes(x = stock, fill = treatment, lty = treatment)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("Original Sample", "Replication Sample")) +
  guides(lty = "none") +
  geom_vline(xintercept = replicationWealth,
             col = "#000000", alpha = 0.5,
             lty = 2) +
  geom_vline(xintercept = originalWealth,
             col = "#000000", alpha = 0.5,
             lty = 1) +
    labs(title = "", 
       y = "", x = "Stock",
       caption = "Grey lines indicate means (dashed line = replication sample).") +
  layout +
  theme(legend.position = "top")
```

@@

Why? Perhaps because the heterogeneity within samples and across groups has been too large to _detect_ a significant difference. The right panel of @fig-growth-heterogeneity depicts heterogeneity: In the replication sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%). More broadly, the replication sample is characterized by inequality between groups ($SD_{Replication} =$ `r rSD`). The same holds true for the original sample ($SD_{Original} =$ `r oSD`). Hence, the heterogeneity across groups does not differ between samples, which is remarkable because the replication sample was drawn from a more heterogeneous (non-convenience sample). Does it differ within groups?

@@

# plot
p1 <- ggplot(data = STOCK, 
             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0, 4700), expand = c(0, 0)) +
  labs(y = "Wealth", x = "Period") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Replication Sample")) +
  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
  annotate("text", x = 9, y = 4630, size = 3,
           label = "max", col = "#b5b5b5") +
  geom_line(data = maxPath, mapping = aes(x = x, y =y), col = "#b5b5b5", lty = 2) +
  guides(fill = "none") +
  layout +
  theme(legend.position = "top") +
  guides(lty = "none")
```

@@

# plot
p2 <- ggplot(data = main,
       mapping = aes(x = round, y = stock, color = treatment, by = groupID)) +
  geom_line(alpha = 0.5) +
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0, 2000),
                       expand = c(0, NA)) +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Replication Sample")) +
  labs(y = "", x = "Period") +
  layout +
  guides(col = "none")

@@

ggplot(data = main,
       mapping = aes(x = gini, fill = treatment, lty = treatment)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, 1),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("Original Sample", "Replication Sample")) +
  guides(lty = "none") +
  geom_vline(xintercept = replicationGini,
             col = "#000000", alpha = 0.5,
             lty = 2) +
  geom_vline(xintercept = originalGini,
             col = "#000000", alpha = 0.5,
             lty = 1) +
    labs(title = "", 
       y = "", x = "Gini Coefficient",
       caption = "Grey lines indicate means (dashed line = replication sample).") +
  layout +
  theme(legend.position = "top")
```

@@

ggplot(data = GINI, 
             aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 0:10) +
  scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
  labs(y = "Wealth", x = "Period") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Replication Sample")) +
  guides(fill = "none") +
  layout +
  theme(legend.position = "top") +
  guides(lty = "none")
```

@@

@fig-kernel-generalizability shows distributions of contributions across both choices for both samples. The top panels illustrate the behavior of the general population sample. The bottom panels illustrate the behavior of the general population sample. The left panels show the behavior in the VCA. The right panels show the behavior in first period of the game. A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA. (c) In contrast to @GKLS2020's observation, we do not observe a difference between samples in the abstract game's contribution behavior. (d) However, the student's share of income contributed to the VCA is significantly lower than the general population sample's contributions (two-sided rank sum test, p=`r rs1`). Taken together, these aggregate results indicate, that the consistency between tasks is higher for the general population than it is for students. Or, to put it differently, the general population's behavior in the abstract game better predicts their behavior in real-world mitigation context.

@@

<!--
@fig-kernel-generalizability also indicates that the general population's contribution behavior is more consistent than the students' behavior. Hence, one may conclude that their behavior in the abstract game translates comparably well to the real world. This is not the case. If anything, the _students'_ behavior in the abstract game is more predictive for their VCA. @fig-scatter-generalizability visualizes the within-subjects relationship of both contribution tasks. More precisely, it shows a scatter plot of realized choices, with the percentage of endowment spent by each participant in the first period of the game on the x-axis and that spent in the VCA on the y-axis. In addition, the figures contains a fitted line of a linear model. The upper pannel illustrates overall behavior and exhibits a slope which is indistinguishable from zero. No matter how much the participants contributed in the first round, they spent, on average, about `r temp[, round(mean(donationShare))]`% of their income on the VCA. The two bottom panels differentiate between both samples with slopes that differ qualitatively. However, none of the slopes is significant. 
-->

@@

p1 <- ggplot(data = STOCKe, 
             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="bottom") +
  # geom_vline(xintercept = 10, alpha = 0.66) +
  geom_line() +
  geom_point() +
  guides(lty = "none", fill = "none") +
  scale_x_continuous(name="",  breaks = 1:10) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Wealth (Equality)", x = "Period") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Replication Sample"))

p2 <- ggplot(data = STOCKu, 
             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="bottom") +
  # geom_vline(xintercept = 10, alpha = 0.66) +
  geom_line() +
  geom_point() +
  guides(lty = "none", fill = "none") +
  scale_x_continuous(name="",  breaks = 1:10) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Wealth (Inequality)", x = "Period") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Replication Sample"))

>>>>

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, may not necessarily prevent us from reaching these targets, but it makes it more difficult in the future. Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals. This applies especially to carbon dioxide emissions where its current stock will last for well over a millennium [@Inman2008; @CalzolariEtAl2018].

@@

Taken together, this study makes three contributions. First, it reproduces parts of GMTV's original experiment and highlights the importance of pure replications. Second, it shows that logistically complex online experiments are feasible for samples other than students or clickworkers. Third, this paper supports critics arguing that findings from abstract games do not generalize well---not even with a more representative sample. After reporting the methods, this paper is organized along these findings.

@@

In fact, the experiment reported in this article qualifies for the label _'pre-registered'_ at a first glance:
Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration]. In addition, I pre-registered the exact analyses I planned to run when I designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]

At a second glance, the analysis that made the most sense after having collected the data and that is reported here is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students which opened up a new research direction: assessing generalizability. Hence, this article combines both confirmatory as well as exploratory research.

Accordingly, I  changed many of the analysis scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent. Importantly, I followed a literate programming approach [@Knuth_1984; @AkhtarYe_2023]. Hence, all documents needed to analyze the data and write the report stem from the same source. This establishes consistence between the commands one tells the statistical software to do and the explanation one tells human beings one told the statistical software to do. As such, (a), (b) and the transition from (a) to (b) are not only transparent but also comprehensible.

@@

In the terminology of @Hamermesh2007, I ran both a _pure_ as well as a _scientific_ reproduction^[@Parsons2022 use the term of a _conceptual replication_ which means the same.] of one treatment of GMTV's dynamic public good game. The pure reproduction re-analyzes the original data. [Appendix A](#A:-Pure-Replication) documents [errors I identified]() in the original paper. The scientific reproduction, where I utilize a different sample drawn from a different population in a different situation, is described in the following sections.

@@

## Pre-registered GMTV Reproduction {#sec-replication}

@@

First, I ask whether the samples differ with respect to their initial contributions to the public good. Is the reproduction sample (consisting of both students and non-students) more pro-social than the original sample? A two-sided rank sum test reveals that it is not (p=`r rs1`). Both samples contributed 10 tokens, that is, 50% of their endowments on average (median and mean). Moreover, both samples' initial contributions resemble initial contributions participants usually make in the static game with partner matching.^[See Figure 3B in @fehrgaechter2000 [p.989], for instance.] However, in the dynamic game presented here, we are particularly interested in the subsequent periods because differences add up exponentially. Do the two groups remain similar over the course of time?

@@

ggplot(data = R1[treatment != "noPunish15"],
       mapping = aes(x = ownContribution, fill = treatment, lty = treatment)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, 20),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, 0.1),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("Original Sample", "Reproduction Sample")) +
  guides(lty = "none") +
  geom_vline(xintercept = R1[treatment == "replication", 
                             mean(ownContribution)],
             col = "#FFFFFF",
             lty = 2) +
  geom_vline(xintercept = R1[treatment == "noPunish10", 
                             mean(ownContribution)],
             col = "#FFFFFF",
             lty = 1) +
    labs(title = "", 
       y = "", x = "Initially Contributed Tokens",
       caption = "White lines indicate means (dashed line = reproduction sample).") +
  layout +
  theme(legend.position = "top")
```

@@

In particular, do the two samples' contributions follow the same path over the 10 periods they played? The answer is _no_. @fig-share-of-contributions illustrates that the samples make similar contributions at the beginning and the end of the game but behave differently in between. More precisely, the left panel--depicting the average contributions in absolute terms--shows that the original sample contributed more than the reproduction sample _in all but the first and last period_.^[In period five, this difference is significant: a two-sided rank sum test yields p=`r rs2`. ] For this reason, the original sample's behavior differs from the reproduction sample's behavior in two aspects: it contributes more and exhibits a considerable drop in the last period (whereas the reproduction sample's contributions flatten).

Note that increasing contributions over time imply increasing endowments over time. Hence, absolute contributions do not tell much about the willingness to cooperate. For this reason, the right panel in @fig-share-of-contributions shows the average _share of endowments contributed_ over time. Both samples exhibit a similar pattern: their share of endowments contributed declined and did not stabilize. However, both samples also differ with respect to one aspect: the reproduction sample's share of contributions declines faster. This is mirrored by a two-sided rank sum test which is only significant at a five percent level in periods three and four.

@@

p1 <- ggplot(data = SUM, 
             aes(x = round, y = contribution, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="top") +
  geom_line(show.legend=FALSE) +
  geom_point() +
  scale_x_continuous(name="",  breaks = 1:15) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Average Amount of Tokens contributed") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Reproduction Sample")) + 
  guides(fill = "none") +
  theme(plot.margin = margin(0.25,1,0.25,0.25, "cm"))

@@

p2 <- ggplot(data = SHARE, 
             aes(x = round, y = share, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="bottom") +
  geom_line(show.legend=FALSE) +
  geom_point() +
  scale_x_continuous(name="",  breaks = 1:15) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Share of Current Endowment contributed") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Reproduction Sample")) +
  guides(fill = "none")

@@

How do the different contribution-paths translate into wealth?^[To measure wealth and growth, I define a variable called _stock_ which sums the endowments of all participants in a given group at the end of the round (that is, after the contributions have been made, multiplied and redistributed).] Given that the original sample contributed more, one would expect the respective groups to be  more wealthy. A mere mean comparison indicates just that: An average group in the original sample accumulated about `r round(originalWealth)` tokens. In contrast, an average group in the reproduction sample accumulated about `r round(replicationWealth)` tokens. This difference is insignificant at conventional levels though: A two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean stock in last period of the game.

@@

ggplot(data = main,
       mapping = aes(x = stock, fill = treatment, lty = treatment)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("Original Sample", "Reproduction Sample")) +
  guides(lty = "none") +
  geom_vline(xintercept = replicationWealth,
             col = "#000000", alpha = 0.5,
             lty = 2) +
  geom_vline(xintercept = originalWealth,
             col = "#000000", alpha = 0.5,
             lty = 1) +
    labs(title = "", 
       y = "", x = "Stock",
       caption = "Grey lines indicate means (dashed line = reproduction sample).") +
  layout +
  theme(legend.position = "top")
```

@@

Why? Perhaps because the heterogeneity within samples and across groups has been too large to _detect_ a significant difference. The right panel of @fig-growth-heterogeneity depicts heterogeneity: In the reproduction sample, the richest group earned `r a <- main[treatment == "replication" & round == 10, max(stock)]; a` tokens (which is about `r round(a/80, digits = 2)*100`% of the initial endowment) whereas the poorest group ends up with `r b <- main[treatment == "replication" & round == 10, min(stock)]; b` tokens (`r round(b/80, digits = 2)*100`%). More broadly, the reproduction sample is characterized by inequality between groups ($SD_{Replication} =$ `r rSD`). The same holds true for the original sample ($SD_{Original} =$ `r oSD`). Hence, the heterogeneity across groups does not differ between samples, which is remarkable because the reproduction sample was drawn from a more heterogeneous (non-convenience sample). Does it differ within groups?

@@

# plot
p1 <- ggplot(data = STOCK, 
             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0, 4700), expand = c(0, 0)) +
  labs(y = "Wealth", x = "Period") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Reproduction Sample")) +
  geom_point(mapping = aes(x = 10, y = 4613), col = "#b5b5b5") +
  annotate("text", x = 9, y = 4630, size = 3,
           label = "max", col = "#b5b5b5") +
  geom_line(data = maxPath, mapping = aes(x = x, y =y), col = "#b5b5b5", lty = 2) +
  guides(fill = "none") +
  layout +
  theme(legend.position = "top") +
  guides(lty = "none")
```

@@

# plot
p2 <- ggplot(data = main,
       mapping = aes(x = round, y = stock, color = treatment, by = groupID)) +
  geom_line(alpha = 0.5) +
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(limits = c(0, 2000),
                       expand = c(0, NA)) +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Reproduction Sample")) +
  labs(y = "", x = "Period") +
  layout +
  guides(col = "none")

@@

ggplot(data = main,
       mapping = aes(x = gini, fill = treatment, lty = treatment)) +
  geom_density(alpha = 0.5) +
  scale_x_continuous(limits = c(0, 1),
                       expand = c(0, NA)) +
  scale_y_continuous(limits = c(0, NA),
                       expand = c(0, NA)) +
  scale_fill_manual(values = c(cPrimary, cSecondary),
                    labels = c("Original Sample", "Reproduction Sample")) +
  guides(lty = "none") +
  geom_vline(xintercept = replicationGini,
             col = "#000000", alpha = 0.5,
             lty = 2) +
  geom_vline(xintercept = originalGini,
             col = "#000000", alpha = 0.5,
             lty = 1) +
    labs(title = "", 
       y = "", x = "Gini Coefficient",
       caption = "Grey lines indicate means (dashed line = reproduction sample).") +
  layout +
  theme(legend.position = "top")
```

@@

ggplot(data = GINI, 
             aes(x = round, y = gini, fill = treatment, color = treatment, lty = treatment)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = 0:10) +
  scale_y_continuous(limits = c(0, 0.25), expand = c(0, 0)) +
  labs(y = "Wealth", x = "Period") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Reproduction Sample")) +
  guides(fill = "none") +
  layout +
  theme(legend.position = "top") +
  guides(lty = "none")
```

@@

@fig-kernel-generalizability shows distributions of contributions across both choices for both samples. The top panels illustrate the behavior of the general population sample. The bottom panels illustrate the behavior of the student sample. The left panels show the behavior in the VCA. The right panels show the behavior in first period of the game. A visual inspection shows that (a) mean contributions are positive in both tasks for both samples.^[The same holds true for median contributions.] (b) Furthermore, average contributions are lower in the VCA. (c) In contrast to @GKLS2020's observation, we do not observe a difference between samples in the abstract game's contribution behavior. (d) However, the student's share of income contributed to the VCA is significantly lower than the general population sample's contributions (two-sided rank sum test, p=`r rs1`). Taken together, these aggregate results indicate, that the consistency between tasks is higher for the general population than it is for students. Or, to put it differently, the general population's behavior in the abstract game better predicts their behavior in real-world mitigation context.

@@

<!--
@fig-kernel-generalizability also indicates that the general population's contribution behavior is more consistent than the students' behavior. Hence, one may conclude that their behavior in the abstract game translates comparably well to the real world. This is not the case. If anything, the _students'_ behavior in the abstract game is more predictive for their VCA. @fig-scatter-generalizability visualizes the within-subjects relationship of both contribution tasks. More precisely, it shows a scatter plot of realized choices, with the percentage of endowment spent by each participant in the first period of the game on the x-axis and that spent in the VCA on the y-axis. In addition, the figures contains a fitted line of a linear model. The upper panel illustrates overall behavior and exhibits a slope which is indistinguishable from zero. No matter how much the participants contributed in the first round, they spent, on average, about `r temp[, round(mean(donationShare))]`% of their income on the VCA. The two bottom panels differentiate between both samples with slopes that differ qualitatively. However, none of the slopes is significant. 
-->

@@

p1 <- ggplot(data = STOCKe, 
             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="bottom") +
  # geom_vline(xintercept = 10, alpha = 0.66) +
  geom_line() +
  geom_point() +
  guides(lty = "none", fill = "none") +
  scale_x_continuous(name="",  breaks = 1:10) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Wealth (Equality)", x = "Period") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Reproduction Sample"))

p2 <- ggplot(data = STOCKu, 
             aes(x = round, y = stock, fill = treatment, color = treatment, lty = treatment)) +
  layout +
  theme(legend.position="bottom") +
  # geom_vline(xintercept = 10, alpha = 0.66) +
  geom_line() +
  geom_point() +
  guides(lty = "none", fill = "none") +
  scale_x_continuous(name="",  breaks = 1:10) +
  scale_y_continuous(limits = c(0, upperLimit), expand = c(0, 0)) +
  labs(y = "Wealth (Inequality)", x = "Period") +
  scale_color_manual(values = c(cPrimary, cSecondary),
                     labels = c("Original Sample", "Reproduction Sample"))
